\documentclass{ubo_tex_uebungszettel/uebungszettel}
\input{config/config.tex}

\title{Zettel 01}
\ausgabe{September 9, 2023}
\abgabe{}
\hinweis{}

\author{Chris Geron \& Adrian Oeyen}



\theoremstyle{definition}
\newtheorem*{story}{Story}

\newcommand{\pp}[1]{\lpl{#1}}
\newcommand{\furl}[1]{\footnote{\url{#1}}}

\begin{document}

\maketitle

\noindent \tb{Note}: \quad
All exercises are intentionally vague and invite you to extend them with any functionality you like.

\noindent For this reason, it is perfectly fine if you do not complete all exercises.

\noindent Some exercises contain references to pre-prepared programs. You can find and download these from this Sciebo-Share\furl{https://uni-bonn.sciebo.de/s/O4bU6jJ8UAN2pFR} in the folder corresponding to the day.

\medskip


\noindent \tb{Setting up the development environment} \quad

    \begin{enumerate}
        \item Familiarize yourself with Python's Virtual Environments\furl{https://docs.python.org/3/library/venv.html} and configure one for your projects in the advanced course.
        \item Go through \pp{pycharm-cheatsheet.pdf} and see which options are of interest to you.
    \end{enumerate}

\medskip
\medskip

\noindent \tb{The Bi-Language} \quad

    \noindent The Bi-Language is a slang which inserts a \glqq bi\grqq~after every vowel.\\
    Example: \glqq Felix\grqq~becomes \glqq Febilibix\grqq.
    \begin{enumerate}
        \item Write a program that converts a given sentence into Bi-Language.
        \item Experiment with different implementations. How many lines do you need?
    \end{enumerate}
\medskip
\medskip

\noindent \tb{Files} \quad\newline
\noindent \tb{Note}: \quad
All steps should obviously be solved using Python. The program should behave the same each time.
\begin{enumerate}
	
	\item Create a Pathlib object \pp{test/} in any folder.
	\item Convert the path to an absolute path.
	\item Append \pp{data/test1/} to the path.
	\item Make sure the path exists.
	\item Create a file \pp{text.txt} in this directory.
	\item Request any input from the console.
	\item Write the input to the file.
	\item Read the content of the file.
	\item Append the line \pp{This text was machine-generated} to the file content.
	\item Verify the correctness of your program by running it multiple times.

\end{enumerate}


\noindent \tb{Comprehensions} \quad

    \noindent The following tasks should be solved using comprehensions. It can be helpful to first solve them using normal loops and then convert them to comprehensions.\\
    \begin{enumerate}
        \item Generate a nested list of the form:
        \item[]\[\begin{matrix}
            [[0 & 1 & 2],\\
            [3 & 4 & 5],\\
            [6 & 7 & 8]]\\
        \end{matrix}\]
        \item Generate a nested list of the form:
        \item[]\[\begin{matrix}
            [[0 & 1 & 0],\\
            [1 & 1 & 1],\\
            [0 & 1 & 0]]\\
        \end{matrix}\]

        \item Create a \pp{dict} from the list of tuples in \pp{comprehension.py}.
    
        \item Count the frequency of each letter in \pp{lorem\_ipsum} in \pp{comprehension.py}.
    \end{enumerate}

\noindent \tb{Hangman} \quad

    \noindent 
    \begin{enumerate}
        \item Using the Random library\furl{https://docs.python.org/3/library/random.html}, create a Hangman\furl{https://en.wikipedia.org/wiki/Hangman_(game)} game which picks a word from a collection and asks the player to guess it.
        \item What would make the game easier to play?
        \item Adapt the system so that the words to guess are read from a file. Use the context manager for this.
        \item Learn about \pp{datetime}\furl{https://docs.python.org/3/library/datetime.html\#datetime-objects} and use it to measure the time spent guessing.
    \end{enumerate}

\medskip
\noindent \tb{PEP8} \quad

    \noindent 
    \begin{enumerate}
        \item Transform the given code \pp{pep8.py} into PEP8-compliant code\footnote{PyCharm and other IDEs provide an autoformatter. It is still recommended to do it manually at least once.}.
        \item Add type hints.
    \end{enumerate}

\medskip
\noindent \tb{Matrix} \quad

\noindent
     Given this matrix implementation in \pp{matrix.py}.
    \begin{enumerate}
        \item Add a properly formatted string representation for the matrix.
        \item Extend it with matrix addition and matrix multiplication\furl{https://peps.python.org/pep-0465/}.
        \item Which other functions could be useful for a matrix?
        \noindent 
    \end{enumerate}

\medskip
\noindent \tb{Debugger} \quad

\noindent
    \begin{enumerate}
        \item Some errors are hidden in \pp{debugging.py}. Use the debugger\furl{https://www.jetbrains.com/help/pycharm/debugging-your-first-python-application.html\#where-is-the-problem} to locate them.
        \noindent 
    \end{enumerate}


\medskip
\noindent \tb{Turtle} \quad


    \noindent Familiarize yourself with the Python Turtle\furl{https://docs.python.org/3/library/turtle.html} library.\\
    Structure your code so that the desired functionality can be easily selected.
    \begin{enumerate}
        \item Draw a square.
        \item Draw an 8-step staircase.
        \item Draw an n-sided polygon, where the number of sides is requested beforehand.
        \item Draw the \textsl{Koch Snowflake}\furl{https://en.wikipedia.org/wiki/Koch_snowflake}.
        \item Draw a \textsl{Fractal Tree}\furl{https://en.wikipedia.org/wiki/Fractal_canopy}.
        \item Can you think of other patterns to draw?
        \noindent 
    \end{enumerate}

    \medskip
\noindent \tb{Finished everything?} \quad
\noindent
    Review your solutions to the previous exercises. How could they be extended or improved? Have you documented everything?
\end{document}
