\documentclass{config/minimal_uebungszettel}
\input{config/config.tex}
\author{Chris Geron}
\tutor{
	Mathilde~Schreck,
	Adrian~Oeyen
}

\title{Pycharm Setup and Cheatsheet}
\ausgabe{}
\abgabe{}
\hinweis{}


\theoremstyle{definition}
\newtheorem*{story}{Story}

\newcommand{\pp}[1]{\lpl{#1}}
\newcommand{\furl}[1]{\footnote{\url{#1}}}

\begin{document}

\maketitle

\noindent \tb{Note}: \quad
This list is far from complete. It is just meant to be a best-off!
\medskip


\noindent \tb{Properly configuring the IDE} \quad

    \begin{enumerate}
        \item adjusting \tb{Commenting / Uncommenting} on a German keyboard and remapping Refactor
        \begin{itemize}
        	\item Open settings: \pp{file/settings}
        	$\rightarrow$ \pp{Keymap}
        	
        	\item search for \pp{line comment}
        	
        	\item[] Choose \pp{Comment with Line Comment} 
        	and set it to something else by double-clicking, e.g. 
        	\pp{cmd+shift+7}\footnote{This shortcut is already taken, but the feature is irrelevant. So just replace it.}.
        	
        \end{itemize}
        
         \item Set \tb{Rename} of a variable to a meaningful default
        \item[] In the \pp{Keymap} settings: search for \pp{Rename} and choose the option under \pp{Refactor}. A possible option is \pp{ctrl+w}. 
        
       \item Enable changing of \tb{font size} using \pp{ctrl+scroll}
       \begin{itemize}
       		\item In the settings under \pp{Editor/General}, check the box at the top for \pp{Change font size...}.
       \end{itemize}
       
      \item If needed: adjust \tb{RAM} allocation
       \begin{itemize}
       	\item \pp{Help} $\rightarrow$ \pp{Change Memory Settings}
       	\item[] The default is 2GB, which should work in most cases.
       \end{itemize}
    \end{enumerate}
    

\noindent \tb{Setting up Virtual Environment\furl{https://docs.python.org/3/library/venv.html} / Interpreter} \quad

\begin{enumerate}
	\item Configure a \pp{venv} in the IDE\footnote{\url{https://www.jetbrains.com/help/pycharm/creating-virtual-environment.html\#existing-virtual-environment}}
	\item The IDE must be told where the root \pp{source-folder}\furl{https://www.jetbrains.com/help/pycharm/configuring-project-structure.html\#mark-dir-project-view} is.
	\begin{itemize}
		\item This is usually the \pp{/src} folder where the actual code resides.
	\end{itemize}
\end{enumerate}
   
\pagebreak


\noindent \tb{Useful UI features} \quad
\begin{itemize}
	\item By right-clicking on a file, it can be executed.
	\item[] Used \pp{Run Configurations} can be selected and configured\footnote{This is the place to define e.g. environment variables or arguments to be passed.} in the top right next to the \pp{Play button}.
	
	\item In the bottom left, you can switch between \pp{Run Console}, a \pp{System Shell}, a \pp{Python Shell}, and more.
	
	\item Obviously, the UI supports multiple editor windows, which can be created via drag-and-drop.
	
	\item By \pp{right-clicking} on a variable, function, or selected block of code, the \pp{Refactor} submenu can be opened. It offers a number of useful features for refactoring code.
	
\end{itemize}

    

\noindent \tb{Useful Shortcuts} \quad

	\begin{itemize}
		\item \pp{ctrl+click}
		\item[] Jump to the \tb{definition} of a function / variable. If you click on the definition itself, all usages will be shown.
		

		\item \pp{ctrl+alt+(arrow right | left)}
		\item[] Allows you to \tb{navigate} through the (cross-file) cursor position history.
		\item[] $\rightarrow$ Very useful when you looked something up and want to go back.
		
		\item \pp{press shift twice}: Opens the \tb{universal search}
		\item[] Most interesting feature: The \pp{Scratch File}, a file that doesn’t clutter your project directory but still has access to the modules in your current project.
		\item[] $\rightarrow$ ideal for quickly testing things.
		
		\item \pp{alt+enter} 
		\item[] Shows context \tb{suggestions} for the current cursor position.
		\item[] $\rightarrow$ Especially useful when something is underlined in red or yellow. Allows, among other things, quick importing of a missing module.
		
		\item \pp{ctrl+p} inside the parentheses of a function call
		\item[] Shows the function signatures.
		
		\item \pp{ctrl+alt+y} in the file window
		\item[] \tb{Reload} files by executing \pp{Reload from Disk}\footnote{See section \glqq Annoying Things\grqq}
		
	\end{itemize}

\pagebreak

\noindent \tb{Annoying Things} \quad

\begin{itemize}
	\item Files created by running programs are only displayed after the program finishes.
	\item[] This is especially annoying with Jupyter Notebooks.
	\item[] $\rightarrow$ One solution is \pp{Right-click} $\rightarrow$ \pp{Reload from Disk} or \pp{ctrl+alt+y}
\end{itemize}	


\end{document}
