\documentclass{config/minimal_uebungszettel}
\input{config/config.tex}

\title{Zettel 05}
\ausgabe{13. September 2023}
\abgabe{}
\hinweis{}


\theoremstyle{definition}
\newtheorem*{story}{Story}

\newcommand{\pp}[1]{\lpl{#1}}
\newcommand{\furl}[1]{\footnote{\url{#1}}}

\begin{document}
	\maketitle


    \noindent \tb{Evaluation}: \quad
	
	\noindent Bitte nehmen Sie sich etwas Zeit, um den Vertiefungskurs zu evaluieren. Dies ist für die Verbessereung und Einrichtung zukünftiger Angebote wichtig:\\
    \underline{\url{https://limesurvey.informatik.uni-bonn.de/index.php/395267?lang=en}}

	\medskip
    \medskip
	
\noindent \tb{Note}: \quad
This worksheet contains more exercises than can likely be completed within the tutorial session.\\
Look through the tasks and start with the ones that interest you most.\\
Feel free to extend or modify the given exercises with any functionality you like.

\medskip

\noindent In some tasks, you will find references to pre-prepared programs. You can find and download them from this Sciebo share\furl{https://uni-bonn.sciebo.de/s/f3yJSCBKiDLHzHS} in the folder of the corresponding day.

\medskip
	
	
\noindent \tb{Setting up your development environment} \quad

\begin{enumerate}
	\item If you have not done so on a previous day, set up a virtual environment and an IDE.\\
	More information can be found on Worksheet 1.
	
	\item Extend your \pp{venv} with the packages \pp{rich}, \pp{pydantic-ai}.
\end{enumerate}

\noindent \tb{Wiki R\textsl{AI}ce}
	\newline
	\noindent Write an Agent that autonomously plays Wiki Race.\\
	If you joined us on Day 2, you probably built your own Wiki Race and had some fun playing it. Now it’s time to pass the fun part -- the actual gameplay -- over to the AI. After all, who needs fun, right?\\
	If you don't know what Wiki Race was, please refer to the exercise sheet from Day 2.
	\\
	Build an Agent that plays Wiki Race for you.
	\\
	Before you start implementing an agent: Go back to the Slide \pp{Abstractions} and plan thse details.
	
	
	Now it's time get started on your code.
	\begin{itemize}
		\item Create the class that models the dependencies the tool execution will need.
		
		\item Create the class that models the answer that is expected from the agent.

		
		\item Implement the tools the agent will need.
		\item[]\begin{itemize}
			\item Make sure to include some logging.
			\item Inlcude some functionality to track the path the agent attempted, e.g. store all searched words that were successful in a list.
			\item It might be useful for testing and development to keep the core functionality in a function that is callable without a \pp{RunContext}, that is then called from the tool-function.
		\end{itemize}
			
			\item Initialize the agent
			
			\begin{itemize}
				\item Write the prompts
				\item Provide it with the tools
				\item Specify the dependency type
				\item Specify the outpt type
				\item Make sure to implement some basic logging to see what your agent is up to
			\end{itemize}
			

			
			\item Run the Agent and keep a close eye on its work
			
			\item Validate if the result the agent produced alignes with the path that you tracked yourself
			
			\item Add some more tracking like: How many steps did the agent need? How many failed tool calls happend?
			
			\item Depending on your tool implementation: Can you save requests with some type of input validation before you call the API?
		\end{itemize}
		
		You can find the API key to try things out in the readme.md.\newline
		Please be careful with your spending. You all share the same budget. There will be \tb{no refill} if the budget is depleted.


\medskip

\newpage
\begin{aufg}[Rich] \quad
	With Rich you can easily create great terminal UIs\footnote{Remember to set the Emulate Terminal option in PyCharm's run configuration if necessary.}. 
	\newline
	Here are some ideas:\newline
	
	\noindent \tb{Colored Text} \quad
	
	\noindent Display Hello World on the console, but in color!
	
	\medskip
	\medskip
	
	\noindent \tb{Pseudo Progress Bar} \quad
	
	\noindent Use Rich to display a progress bar that convincingly moves forward as if it were actually loading something. You can use the random library to generate a random wait time / random progress. Experiment a little with the values.\newline
	Note: It may feel better if you generate multiple random numbers at once and combine them.
	
	\medskip
	\medskip
	
	\noindent \tb{Layout} \quad
	
	\noindent Create a layout with multiple sections and fill them with any elements.
	
	\medskip
	\medskip
	
	\noindent \tb{Live} \quad
	
	Create a live layout in which you display changing content.\newline
	Possible contents could be:
	\begin{itemize}
		\item The current time
		\item A text that builds up word by word
		\item A continuously fast-incrementing number
		\item A simple counter that increments each time the UI refreshes
	\end{itemize}
	
	\medskip
	\medskip
	
	\noindent \tb{Custom Renderables} \quad
	
	\noindent Write your own class that implements \pp{__rich__}. Think of some possible content and add the element to your live UI.\newline
	Note: For example, you could simply rewrite elements from the previous task to use \pp{__rich__}.
	
	\medskip
	\medskip
	
	\noindent \tb{Discord Overview (Extreme Skill Level Increase)} \quad
	
	\noindent Write a UI that shows you a preview of new messages in the channels of a Discord server.
	\begin{itemize}
		\item The layout could show an overview of the channels on the left -- similar to Discord’s own UI -- and “rotate through” them.
		\item The main window could display the history of the latest messages in the current channel.
	\end{itemize}
	
\end{aufg}

	
\end{document}
