\documentclass{config/minimal_uebungszettel}
\input{config/config.tex}

\title{Exercise 03}
\ausgabe{september 10. 2025}
\abgabe{}
\hinweis{}


\theoremstyle{definition}
\newtheorem*{story}{Story}

\newcommand{\pp}[1]{\lpl{#1}}
\newcommand{\furl}[1]{\footnote{\url{#1}}}

\begin{document}

\maketitle

\noindent \tb{Note}: \quad
This worksheet contains more exercises than can likely be completed within the tutorial session.\\
Look through the tasks and start with the ones that interest you most.\\
Feel free to extend or modify the given exercises with any functionality you like.

\medskip

\noindent In some tasks, you will find references to pre-prepared programs. You can find and download them from this Sciebo share\furl{https://uni-bonn.sciebo.de/s/f3yJSCBKiDLHzHS} in the folder of the corresponding day.

\medskip


\noindent \tb{Setting up your development environment} \quad

    \begin{enumerate}
        \item If you have not done so on a previous day, set up a virtual environment and an IDE.\\
        More information can be found on Worksheet 1.

        \item Extend your \pp{venv} with the packages \pp{numpy}, \pp{pandas}, and \pp{matplotlib}.
    \end{enumerate}

\medskip
\medskip

\medskip
\noindent \tb{NumPy Warmup} \quad
  
    \noindent The following exercises will help you get familiar with the basics of NumPy.

    \begin{enumerate}

            \item Create a NumPy array of integers from 1 to 10 and calculate the sum, average, and standard deviation of the array.
            
            \item Generate a random $5 \times 5$ matrix using NumPy and find the maximum and minimum values in the matrix.
            
            \item Create a NumPy array of shape $(3, 4)$ filled with random floating-point numbers between 0 and 1. Reshape the array into a $(4, 3)$ array and output its transpose.
            
            \item Create two NumPy arrays of shape $(3, 3)$ and perform element-wise addition, subtraction, multiplication, and division.
            
            \item Generate a NumPy array with 100 random integers between 1 and 1000. Find the indices of the five largest values in the array.
            
            \item Create a NumPy array of shape $(4, 4)$ with values from 1 to 16. Extract the diagonal elements and calculate their sum.
            
            \item Compute the dot product of two NumPy arrays with shapes $(2, 3)$ and $(3, 2)$.
            
            \item Create a NumPy array of shape $(5, 5)$ where all elements are 0. Replace the diagonal elements with the numbers 1 through 5.
            
            \item Generate a NumPy array with 20 random numbers between -10 and 10. Replace all negative numbers with 0 and output the resulting array.
            
            \item Create a NumPy array of shape $(6, 6)$ with random integers between 1 and 10. Sort each row of the array in ascending order.
            
            \item Create a NumPy array with 30 random integers between 0 and 20. Find all positions that contain the value 7. Which ones are they, and how many?
    \end{enumerate}

    
\medskip
\noindent \tb{Matrix II} \quad

\noindent Revisit the Matrix exercise from Day 1. Use your newly acquired knowledge about \pp{slice} to extract sub-matrices from the matrix with \pp{__get_item__()}.\\
Extend the functionality afterwards also for \pp{__set_item__()}.

\medskip

\medskip
\noindent \tb{Env Variables and Argparser } \quad

\noindent Consider which of your programs from today or previous days could benefit from \pp{env} variables or the \pp{Argparser}.\\
For example, in Hangman you could set the file with the words to be used via an \pp{env} variable or pass it as an argument. 

\medskip
\noindent \tb{Logging} \quad

\begin{enumerate}
    \item Set up a logging configuration consisting of a \pp{FileHandler} and a \pp{StreamHandler}.
    \item Configure the system so that \pp{error} and above are shown in the console, and everything from \pp{info} is stored in the file.
    \item Ensure that the file is placed in a \pp{data/} folder.
    \item[] Make sure that the folder is created if it does not already exist.
\end{enumerate}

\pagebreak

\medskip
\noindent \tb{Sieve of Eratosthenes} \quad
  
    \noindent
    In this task, your goal is to compute all prime numbers up to a given number \pp{N}.\\
    The Sieve of Eratosthenes is a simple but efficient method for doing so.\\
    The goal is to end up with an array that contains \pp{True} at all prime number indices and \pp{False} everywhere else.\\

    The following steps need to be carried out:
    \begin{enumerate}
        \item First, create a \pp{numpy} array of length \pp{n+1}, completely filled with \pp{True} or \pp{1}.
        \item Set the elements at indices \pp{0, 1} to \pp{False}, since 1 and 0 are not prime numbers.

        \item Set all multiples of the value 2 to \pp{False}.
        \item Repeat the same step for all indices $3\leq i \leq \sqrt{n}$ where the array entry is \pp{True}, since multiples of a value can never be prime.
        \item All remaining indices set to \pp{True} are prime numbers.
        \item Find an elegant way, using this boolean array, to compute the indices (i.e., the actual numbers) corresponding to these positions.
        \item Output the result.  
    \end{enumerate}
    Hint: You only need one \pp{for} loop to solve the task. All other operations can be implemented using NumPy.


    \medskip
    \noindent \tb{Fun with Matplotlib} \quad
      
        \noindent
        Let’s have some fun with cool functions and analyze them interactively.\\
        
        \begin{enumerate}
            \item Revisit the interactive example from the lecture.
            \item Plot the function $y = x \cdot \sin(1/x)$
            \item Add interactive sliders for $x$. How does the function change?
            \item Plot two sine functions.
            \item Add a parameter for setting an offset to your sine function, controllable via a slider.
            \item Enjoy the satisfying effect of sine waves sliding against each other!
            \item What other functions and parameters can you plot or change?
        \end{enumerate}

        \noindent \tb{The Weather} \quad
    
\noindent
\begin{enumerate}
    \item Get familiar with the \pp{open-metero} API\furl{https://open-meteo.com/}.
    \item Query the weather and create meaningful plots from the received data.
\end{enumerate}

    \pagebreak

    \medskip
    \noindent \tb{Real Data Analysis} \quad
      
        \noindent
        In this exercise, you will analyze a real dataset. For this purpose, you are given the datasets \pp{boulders\_habitat\_bonn.csv} and \pp{boulders\_habitat\_beuel.csv}\footnote{The 2023 versions are only half the size and may be better suited for slower systems.}. These contain data on the usage of the two Bonn bouldering gyms from May 2022 to today.\\

        \noindent Note: It might make sense to solve this task in a Jupyter notebook.

        \begin{enumerate}
            \item Get familiar with \pp{read_csv}\furl{https://pandas.pydata.org/docs/reference/api/pandas.read_csv.html} from pandas and load one of the datasets into a \pp{DataFrame} from the given CSV file.\\
            The following steps can be performed directly when loading, or afterwards:

            \item \begin{itemize}
                \item Convert the first column to \pp{Integer} and the second to \pp{datetime} objects.
                \item Set the \pp{datetime} column as the index.
                \item The third column is not needed.
            \end{itemize}

            \item Initial analysis:\\
            Use \pp{.describe()} to get a first overview of the dataset.
            
            
            \item The dataset has a density of one data point every five minutes, which is quite large.
            Therefore, calculate the average for each hour.\\
            This can be done with \pp{.resample("30min").mean()}\furl{https://pandas.pydata.org/docs/reference/api/pandas.DataFrame.resample.html\#pandas.DataFrame.resample}.

            \item Repeat the same steps for the second dataset.
            
            \item Merge the two datasets grouped by time.
            
            \item[] You can perform all the following analyses either for both gyms or just for the one of your choice.

            \item Which half-hour period(s) had the highest usage overall? Were they the same in Bonn and Beuel?
            
            \item Extract the data for your birthday. What was the hourly usage on that day?\\
            \item[] Plot the course of the day.
            \item[] Then wonder why all those people weren’t at your birthday party.
            
            \item After overcoming this minor existential crisis: Is there an hour that has the lowest average usage?
            
            \item Are there days with no or very few data points?\\
            Group the unaggregated data by day and count the entries per day.\\
            Note: You can access the date attribute of a \pp{datetime} object with \pp{.date}.
            
            \item Group the data by the time of the index.\\
            Iterate over the time slots and calculate the average usage. Which time slot is the most popular?\\
            Does this observation match your finding about the half-hour with the highest usage?\\
            Note: You can access the time attribute of a \pp{datetime} object with \pp{.time}.
            
            \item Create a bar plot showing the average usage for each half-hour period.
            
            \item Do you notice any other interesting analyses? Let your creativity run free! How about a comparison between the years?

        \end{enumerate}



\end{document}
